---
title: "concatenate_trial_measures"
author: "Savannah McNair"
date: "2025-01-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

necessary packages
```{r}
library(dplyr)
```

Load in your paths:
directory_path is where you have saved your summary stats or trial measures data (the folder where the original data is downloaded to)
output_path is where you would like the outputs to get saved
```{r}
#SM set to the location you downloaded the EEG files to. If you are using a Windows computer, you will need to change the direction of the slashes from '\' to '/'
directory_path <- "X:/Projects/hbcd/EEG/Main_Study/CBRAIN_8.14/" 
output_path <- "Z:/Dropboxes/tmahesh/data release csvs/"
```

set cwd (current working directory) to file path, get a list of IDs 
```{r}
setwd(directory_path)
cwd <- directory_path
dccids <- list.files()
```

create sheets - these are the sheets this script will output
```{r}
FACE_trialmeasures <- NULL
MMN_trialmeasures <- NULL
```

for each folder (ID), pull trial stats by task and condition
#change names of files to new names!!!
```{r}
#for x (each ID), pull out the trial measure data (by task) and paste it into a new sheet, storing ID in a new column
for (x in dccids) {
  processed_data <- paste(x, "/ses-V03/eeg/processed_data", sep="")
  
  # RS_power_file <- paste(cwd, processed_data, "/", x, "_ses-V03_task-RS_Power-summaryStats.csv", sep="")
  # if (file.exists(RS_power_file)) {
  #   RS_power_sheet <- read.csv(RS_power_file)
  #   for (i in 1:nrow(RS_power_sheet)) {
  #     row <- RS_power_sheet[i, , drop = FALSE]
  #     RS_power <- rbind(RS_power, row)
  #   }
  # } else {
  #   message(paste("RS Power file not found for", x))
  # }
  
  FACE_trialmeasures_file <- paste(cwd, processed_data, "/", x, "_ses-V03_task-FACE_ERP-trialMeasures.csv", sep="")
  if (file.exists(FACE_trialmeasures_file)) {
    FACE_trialmeasures_sheet <- read.csv(FACE_trialmeasures_file)
    for (i in 1:nrow(FACE_trialmeasures_sheet)) {
      #FACE_trialmeasures_sheet$ID <- x
      row <- FACE_trialmeasures_sheet[i, , drop = FALSE]
      FACE_trialmeasures <- rbind(FACE_trialmeasures, row)
    }
  } else {
    message(paste("FACE file not found for", x))
  }
  
  MMN_trialmeasures_file <- paste(cwd, processed_data, "/", x, "_ses-V03_task-MMN_ERP-trialMeasures.csv", sep="")
  if (file.exists(MMN_trialmeasures_file)) {
    MMN_trialmeasures_sheet <- read.csv(MMN_trialmeasures_file)
    for (i in 1:nrow(MMN_trialmeasures_sheet)) {
      #MMN_trialmeasures_sheet$ID <- x
      row <- MMN_trialmeasures_sheet[i, , drop = FALSE]
      MMN_trialmeasures <- rbind(MMN_trialmeasures, row)
    }
  } else {
    message(paste("MMN file not found for", x))
  }
}

```

output the dataframes containing concatenated summary stats as a csv
```{r}
write.csv(FACE_trialmeasures, paste(output_path, "FACE_trialMeasures.csv", sep = "")) 
write.csv(MMN_trialmeasures, paste(output_path, "MMN_trialMeasures.csv", sep = ""))
```