---
title: "get_mmn_outputs"
author: "Savannah McNair"
date: "2025-02-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load in your paths:
directory_path is where you have saved your summary stats or trial measures data (the folder where the original data is downloaded to)
output_path is where you would like the outputs to get saved
```{r}
#SM set to the location you downloaded the EEG files to. If you are using a Windows computer, you will need to change the direction of the slashes from '\' to '/'
directory_path <- "X:/Projects/hbcd/EEG/Main_Study/CBRAIN_Outputs/DataReleaseIDs/"
output_path <- "Z:/Dropboxes/SMcNair/SMcNair_Playground/HBCD/Data Release/DataRelease_Githhub/test_cbrain_datarelease_deid/"
```

set cwd (current working directory) to file path, get a list of IDs
```{r}
setwd(directory_path) 
cwd <- directory_path
dccids <- list.files()
```

create sheets - these are the sheets this script will output
```{r}
MMN_ERP <- NULL
```


for each folder (ID), pull summary stats by task and condition
```{r}
#for x (each ID), pull out the MMN ERP data and paste it into a new sheet, storing ID in a new column
for (x in dccids) {
  processed_data <- paste(x, "/ses-V03/eeg/processed_data", sep="")
  
 MMN_ERP_file <- paste(cwd, processed_data, "/", x, "_ses-V03_task-MMN_ERPSummaryStats.csv", sep="")
  if (file.exists(MMN_ERP_file)) {
    MMN_ERP_sheet <- read.csv(MMN_ERP_file)
    for (i in 1:nrow(MMN_ERP_sheet)) {
      MMN_ERP_sheet$ID <- x #paste the DCCID for each row into MMN_ERP_sheet
      row <- MMN_ERP_sheet[i, , drop = FALSE]
      MMN_ERP <- rbind(MMN_ERP, row)
    }
  } else {
    message(paste("MMN ERP file not found for", x))
  }
  
}
```

output the dataframe containing concatenated summary stats as a csv
```{r}
write.csv(MMN_ERP,paste(output_path,"MMN_ERP.csv", sep="")) #Feel free to change the name of the file to however you would prefer it to be named, as a general example we have chosen "MMN_ERP.csv"
```

Output Guide:

Column X: rows for each table (generated by R)
Condition: The condition trials and SME are being reported on (deviant, predeviant, standard for MMN)
SME_200.400_t7t8: Standard measurement error at the t7t8 cluster for the 200-400ms time range
SME_200.400_f7f8: Standard measurement error at the f7f8 cluster for the 200-400ms time range
SME_200.400_fcz: Standard measurement error at the fcz cluster for the 200-400ms time range
ID: participant ID

For more information on measures and outputs consult our documentation, links available in the main Github README
