---
title: "Separate_Conditions"
author: "Trisha Maheshwari"
date: "2025-01-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load in files for each task with conditions (FACE, MMN)
Note: You can either load in cumulative summary stats or cumulative trial measures csvs
```{r}
Face_sumstats <- read.csv("Z:/Dropboxes/tmahesh/data release csvs/FACE_SME.csv")
MMN_sumstats <- read.csv("Z:/Dropboxes/tmahesh/data release csvs/MMN_SME.csv")
```


subset file by conditions for FACE
```{r}
FACE_uprightInv = subset(Face_sumstats, Condition == "uprightInv")
FACE_uprightInv = subset(FACE_uprightInv, select = -X)
FACE_uprightObj = subset(Face_sumstats, Condition == "uprightObj")
FACE_uprightObj = subset(FACE_uprightObj, select = -X)
FACE_object = subset(Face_sumstats, Condition == "object")
FACE_object = subset(FACE_object, select = -X)
FACE_inverted = subset(Face_sumstats, Condition == "inverted")
FACE_inverted = subset(FACE_inverted, select = -X)
```


subset file by conditions for MMN
```{r}
MMN_standard = subset(MMN_sumstats, Condition == "standard")
MMN_standard = subset(MMN_standard, select = -X)
MMN_deviant = subset(MMN_sumstats, Condition == "deviant")
MMN_deviant = subset(MMN_deviant, select = -X)
MMN_predev = subset(MMN_sumstats, Condition == "predeviant")
MMN_predev = subset(MMN_predev, select = -X)
```

write out tables
```{r}
write.csv(FACE_uprightInv, "Z:/Dropboxes/tmahesh/data release csvs/FACE_uprightInv.csv")
write.csv(FACE_uprightObj, "Z:/Dropboxes/tmahesh/data release csvs/FACE_uprightObj.csv")
write.csv(FACE_object, "Z:/Dropboxes/tmahesh/data release csvs/FACE_object.csv")
write.csv(FACE_inverted, "Z:/Dropboxes/tmahesh/data release csvs/FACE_inverted.csv")
```

```{r}

write.csv(MMN_standard, "Z:/Dropboxes/tmahesh/data release csvs/MMN_standard.csv")
write.csv(MMN_deviant, "Z:/Dropboxes/tmahesh/data release csvs/MMN_deviant.csv")
write.csv(MMN_predev, "Z:/Dropboxes/tmahesh/data release csvs/MMN_predev.csv")
```

Output guide:

column X: rows for each table (generated by R)
Condition: type of condition saved
NTrials: how many trials were saved for that participant
ID: participant ID
SME: Standard measurement error (varying by task, time windows, and region of interest)

