---
title: "Separate_Conditions"
author: "Trisha Maheshwari"
date: "2025-01-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load in your paths
directory path is where you have saved your summary stats or trial measures data
output path is where you would like the outputs to get saved
```{r}
#set to the location you downloaded the EEG files to. If you are using a Windows computer, you will need to change the direction of the slashes from '\' to '/'
directory_path <- "Z:/Dropboxes/tmahesh/data release csvs/"
output_path <- "Z:/Dropboxes/tmahesh/data release csvs/"
```


Load in files for each task with conditions (FACE, MMN)
Note: You can either load in concatenated summary stats or concatenated trial measures csvs
```{r}
Face_sumstats <- read.csv(paste(directory_path, "FACE_SME.csv", sep = ""))
MMN_sumstats <- read.csv(paste(directory_path, "MMN_SME.csv", sep = ""))
```


subset file by conditions for FACE
```{r}
FACE_uprightInv = subset(Face_sumstats, Condition == "uprightInv")
FACE_uprightInv = subset(FACE_uprightInv, select = -X) #remove extra column
FACE_uprightObj = subset(Face_sumstats, Condition == "uprightObj")
FACE_uprightObj = subset(FACE_uprightObj, select = -X)
FACE_object = subset(Face_sumstats, Condition == "object")
FACE_object = subset(FACE_object, select = -X)
FACE_inverted = subset(Face_sumstats, Condition == "inverted")
FACE_inverted = subset(FACE_inverted, select = -X)
```


subset file by conditions for MMN
```{r}
MMN_standard = subset(MMN_sumstats, Condition == "standard")
MMN_standard = subset(MMN_standard, select = -X) #remove extra column
MMN_deviant = subset(MMN_sumstats, Condition == "deviant")
MMN_deviant = subset(MMN_deviant, select = -X)
MMN_predev = subset(MMN_sumstats, Condition == "predeviant")
MMN_predev = subset(MMN_predev, select = -X)
```

write out tables
```{r}
write.csv(FACE_uprightInv, paste(output_path, "FACE_uprightInv.csv", sep = ""))
write.csv(FACE_uprightObj, paste(output_path, "FACE_uprightObj.csv", sep= ""))
write.csv(FACE_object, paste(output_path, "FACE_object.csv", sep = ""))
write.csv(FACE_inverted, paste(output_path, "FACE_inverted.csv", sep = ""))
```

```{r}

write.csv(MMN_standard, paste(output_path, "MMN_standard.csv", sep = ""))
write.csv(MMN_deviant, paste(output_path, "MMN_deviant.csv", sep = ""))
write.csv(MMN_predev, paste(output_path, "MMN_predev.csv", sep = ""))
```

Output guide:

column X: rows for each table (generated by R)
Condition: type of condition saved
NTrials: how many trials were saved for that participant
ID: participant ID
SME: Standard measurement error (varying by task, time windows, and region of interest)

